### 2023-03-13 main/chapter_2ljets.tex
add mc citations

\begin{sidewaystable}[tp]
\begin{center}
\scriptsize
\begin{tabular}{llllll}
Physical process &  Generator  & Parton & Cross-section & Tune & PDF set\\
                &             & shower & order in pQCD &      &
\\[0.2em]
\hline
\\[0.2em]
$\ttbar$~\cite{ATL-PHYS-PUB-2016-004}         & \powhegbox\,v2~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd}    & \pythia\,8.230~\cite{Sjostrand:2014zea} & NNLO+NNLL~\cite{ttbarxsec1,ttbarxsec2,ttbarxsec3,ttbarxsec4,ttbarxsec5}                   & A14~\cite{ATL-PHYS-PUB-2014-021}   & \textsc{NNPDF2.3lo}~\cite{Ball:2012cx}\\
$Wt$~\cite{ATL-PHYS-PUB-2016-004}  & \powhegbox\,v2    & \pythia\,8.230 & NNLO+NNLL~\cite{Kidonakis:2010b,Kidonakis:2010tc,Kidonakis:2011wy,Frederix:2012dh}        &A14    & \textsc{NNPDF3.0nlo}~\cite{Ball:2014uwa}\\
$VV$~\cite{ATL-PHYS-PUB-2016-002} & \sherpa\,2.2.2~\cite{Bothmann:2019yzt} & \sherpa\,2.2.2 & NLO~\cite{diboson1,diboson2} & \textsc{Sherpa}\ default & \textsc{NNPDF3.0nnlo} \\
$Z/\gamma^{*}(\rightarrow \ell \ell)$\,+\,jets~\cite{ATL-PHYS-PUB-2016-003}& \sherpa\,2.2.1           & \sherpa\,2.2.1  &NNLO~\cite{DYNNLO1,DYcrosssection}       & \textsc{Sherpa}\ default     &\textsc{NNPDF3.0nnlo}\\
Higgs ($\ttbar h$) & \powhegbox\,v2    & \pythia\,8.230 & NLO~\cite{deFlorian:2016spz} & A14    & \textsc{NPDF2.3lo}\\
Higgs (VBF, $Vh$) & \powhegbox\,v2     & \pythia\,8.212 & NNLO~\cite{deFlorian:2016spz} & AZNLO~\cite{STDM-2012-23} &  \textsc{CTEQ6L1}~\cite{Pumplin:2002vw} \\
Higgs (ggF) & \powhegbox\,v2     & \pythia\,8.212 & NNNLO~\cite{deFlorian:2016spz} & AZNLO & \textsc{CTEQ6L1} \\
$ttt$, $tttt$, $\ttbar$\,+\,$WW$ & \amcatnlo~\cite{Alwall:2014hca} & \pythia\,8.186~\cite{Skands:2014pea} & NLO~\cite{Frederix:2017wme,Alwall:2014hca} & A14 & \textsc{NNPDF2.3lo}\\
$\ttbar$\,+\,$V$~\cite{ATL-PHYS-PUB-2016-005,Garzelli:2012bn}& \amcatnlo        & \pythia\,8.210 & NLO~\cite{Campbell:2012,Lazopoulos:2008,Alwall:2014hca} & \textsc{A14} & \textsc{NNPDF2.3lo}\\
$VVV$~\cite{ATL-PHYS-PUB-2016-002} & \sherpa\,2.2.2 & \sherpa\,2.2.2 &  NLO~\cite{Bothmann:2019yzt} & \textsc{Sherpa}\ default     & \textsc{NNPDF3.0nnlo}\\
\end{tabular}
\caption{%
Caption TODO
% TODO define VBF
% TODO rewrite
% Simulated background event samples used in this analysis with the corresponding matrix element and parton shower generators,
% cross-section order in perturbative QCD used to normalize the event yield, underlying-event tune and PDF set.
% $V$ represents either a $W$ or $Z$ boson.%
}
\label{tab:2ljets_paper_mc}
\end{center}
\end{sidewaystable}

>>>>

\begin{sidewaystable}[tp]
\begin{center}
\scriptsize
\begin{tabular}{llllll}
Physical process &  Generator  & Parton & Cross-section & Tune & PDF set\\
                &             & shower & order in pQCD &      &
\\[0.2em]
\hline
\\[0.2em]
$\ttbar$~\cite{ATL-PHYS-PUB-2016-004}
    & \powhegbox\,v2~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
    & \pythia\,8.230~\cite{Sjostrand:2014zea}
    & NNLO+NNLL~\cite{ttbarxsec1,ttbarxsec2,ttbarxsec3,ttbarxsec4,ttbarxsec5}
    & A14~\cite{ATL-PHYS-PUB-2014-021}
    & \textsc{NNPDF2.3lo}~\cite{Ball:2012cx}
\\
$Wt$~\cite{ATL-PHYS-PUB-2016-004}
    & \powhegbox\,v2
    & \pythia\,8.230
    & NNLO+NNLL~\cite{Kidonakis:2010b,Kidonakis:2010tc,Kidonakis:2011wy,Frederix:2012dh}
    & A14
    & \textsc{NNPDF3.0nlo}~\cite{Ball:2014uwa}
\\
$VV$~\cite{ATL-PHYS-PUB-2016-002}
    & \sherpa\,2.2.2~\cite{Bothmann:2019yzt}
    & \sherpa\,2.2.2 & NLO~\cite{diboson1,diboson2}
    & \textsc{Sherpa}~default
    & \textsc{NNPDF3.0nnlo}
\\
$Z/\gamma^{*}(\rightarrow \ell \ell)$\,+\,jets~\cite{ATL-PHYS-PUB-2016-003}
    & \sherpa\,2.2.1
    & \sherpa\,2.2.1
    & NNLO~\cite{DYNNLO1,DYcrosssection}
    & \textsc{Sherpa}~default
    &\textsc{NNPDF3.0nnlo}
\\
Higgs ($\ttbar h$)
    & \powhegbox\,v2
    & \pythia\,8.230
    & NLO~\cite{deFlorian:2016spz}
    & A14
    & \textsc{NPDF2.3lo}
\\
Higgs (VBF, $Vh$)
    & \powhegbox\,v2
    & \pythia\,8.212
    & NNLO~\cite{deFlorian:2016spz}
    & AZNLO~\cite{STDM-2012-23}
    & \textsc{CTEQ6L1}~\cite{Pumplin:2002vw}
\\
Higgs (ggF)
    & \powhegbox\,v2
    & \pythia\,8.212
    & NNNLO~\cite{deFlorian:2016spz}
    & AZNLO
    & \textsc{CTEQ6L1}
\\
$ttt$, $tttt$, $\ttbar$\,+\,$WW$
    & \amcatnlo~\cite{Alwall:2014hca}
    & \pythia\,8.186~\cite{Skands:2014pea}
    & NLO~\cite{Frederix:2017wme,Alwall:2014hca}
    & A14
    & \textsc{NNPDF2.3lo}
\\
$\ttbar$\,+\,$V$~\cite{ATL-PHYS-PUB-2016-005,Garzelli:2012bn}
    & \amcatnlo
    & \pythia\,8.210
    & NLO~\cite{Campbell:2012,Lazopoulos:2008,Alwall:2014hca}
    & \textsc{A14}
    & \textsc{NNPDF2.3lo}
\\
$VVV$~\cite{ATL-PHYS-PUB-2016-002}
    & \sherpa\,2.2.2
    & \sherpa\,2.2.2
    &  NLO~\cite{Bothmann:2019yzt}
    & \textsc{Sherpa}~default
    & \textsc{NNPDF3.0nnlo}
\\
\end{tabular}
\caption{%
Caption TODO
% TODO import citations
% TODO rewrite
% TODO define VBF
% Simulated background event samples used in this analysis with the corresponding matrix element and parton shower generators,
% cross-section order in perturbative QCD used to normalize the event yield, underlying-event tune and PDF set.
% $V$ represents either a $W$ or $Z$ boson.%
Adapted from~\cite{atlas2022searches}.
}
\label{tab:2ljets_paper_mc}
\end{center}
\end{sidewaystable}
